Results

### 2025-01-14 Analysis/04_Summarise_results.Rmd
tmp UP
need to finish the plotting bit

```{r, echo = FALSE}
## Extracting all the scaled results
scaled_results_2d <- extract.table(all_results_2d, scale.method = "between")
scaled_results_3d <- extract.table(all_results_3d, scale.method = "between")
scaled_results_4d <- extract.table(all_results_4d, scale.method = "between")
scaled_results_5d <- extract.table(all_results_5d, scale.method = "between")
scaled_results_8d <- extract.table(all_results_8d, scale.method = "between")
scaled_results_emp<- extract.table(empirical_results, scale.method = "between")

## Extracting all the results but not centred (still scaled)
raw_results_2d <- extract.table(all_results_2d, scale.method = "between", centre = FALSE)
raw_results_3d <- extract.table(all_results_3d, scale.method = "between", centre = FALSE)
raw_results_4d <- extract.table(all_results_4d, scale.method = "between", centre = FALSE)
raw_results_5d <- extract.table(all_results_5d, scale.method = "between", centre = FALSE)
raw_results_8d <- extract.table(all_results_8d, scale.method = "between", centre = FALSE)
raw_results_emp<- extract.table(empirical_results, scale.method = "between", centre = FALSE)
```

@@

```{r, echo = FALSE}
## Slope and R2 for each model
model_fits_2d  <- lapply(scaled_results_2d, fit.model.rm)
model_fits_3d  <- lapply(scaled_results_3d, fit.model.rm)
model_fits_4d  <- lapply(scaled_results_4d, fit.model.rm)
model_fits_5d  <- lapply(scaled_results_5d, fit.model.rm)
model_fits_8d  <- lapply(scaled_results_8d, fit.model.rm)
model_fits_emp <- lapply(scaled_results_emp, fit.model.rm)

@@

## Making the fancy tables for the models
model_table_2d  <- fancy.table(model_fits_2d, columns = list(c(3,4), 5))
model_table_3d  <- fancy.table(model_fits_3d, columns = list(c(3,4), 5))
model_table_4d  <- fancy.table(model_fits_4d, columns = list(c(3,4), 5))
model_table_5d  <- fancy.table(model_fits_5d, columns = list(c(3,4), 5))
model_table_8d  <- fancy.table(model_fits_8d, columns = list(c(3,4), 5))
model_table_emp <- fancy.table(model_fits_emp, columns = list(c(3,4), 5))
## For the differences
columns_diff_ses <- list(c(1,3), 4)
columns_diff_ses <- c(columns_diff_ses,
                      lapply(columns_diff_ses, `+`, 4),
                      lapply(columns_diff_ses, `+`, 8),
                      lapply(columns_diff_ses, `+`, 12))
null_table_2d   <- fancy.table(null_differences_2d, columns = columns_diff_ses, digits = 2)
null_table_3d   <- fancy.table(null_differences_3d, columns = columns_diff_ses, digits = 2)
null_table_4d   <- fancy.table(null_differences_4d, columns = columns_diff_ses, digits = 2)
null_table_5d   <- fancy.table(null_differences_5d, columns = columns_diff_ses, digits = 2)
null_table_8d   <- fancy.table(null_differences_8d, columns = columns_diff_ses, digits = 2)
null_table_emp  <- fancy.table(null_differences_emp, columns = list(c(1,3), 4, c(1,3)+4, 4+4), digits = 2)
```

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
col_vector <- c(rep("darkgreen", 4), # The regularity ones
                rep("orange", 4), # The divergence ones
                rep("blue", 4)) # The richness ones
## The plot
fancy.plot(scaled_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names, pch = rep(19,4), xlab = "scaled metric change")

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_2d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names, pch = rep(19,4))
dev.off()
```

@@

```{r}
## The plot
fancy.plot(scaled_results_3d, col = col_vector, lm = model_fits_3d, null = null_differences_3d, metric.names = fancy_names, pch = rep(19,4))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_3d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_3d, col = col_vector, lm = model_fits_3d, null = null_differences_3d, metric.names = fancy_names, pch = rep(19,4))
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_results_4d, col = col_vector, lm = model_fits_4d, null = null_differences_4d, metric.names = fancy_names, pch = rep(19,4))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_4d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_4d, col = col_vector, lm = model_fits_4d, null = null_differences_4d, metric.names = fancy_names, pch = rep(19,4))
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_results_5d, col = col_vector, lm = model_fits_5d, null = null_differences_5d, metric.names = fancy_names, pch = rep(19,4))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_5d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_5d, col = col_vector, lm = model_fits_5d, null = null_differences_5d, metric.names = fancy_names, pch = rep(19,4))
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_results_8d, col = col_vector, lm = model_fits_8d, null = null_differences_8d, metric.names = fancy_names, pch = rep(19,4))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_8d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_8d, col = col_vector, lm = model_fits_8d, null = null_differences_8d, metric.names = fancy_names, pch = rep(19,4))
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_results_emp, col = col_vector, lm = NULL, null = null_differences_emp, metric.names = fancy_names, pch = c(19,15,17))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_emp.pdf", height = 11, width = 3.5)
fancy.plot(scaled_results_emp, col = col_vector, lm = NULL, null = null_differences_emp, metric.names = fancy_names, pch = c(19,15,17))
dev.off()
```

@@

@@

pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_2d.pdf", height = 11, width = 8.5)
fancy.plot(raw_results_2d, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = rep(19,5), xlab = "scaled metric", xlim = c(0,1))
dev.off()

pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_4d.pdf", height = 11, width = 8.5)
fancy.plot(raw_results_4d, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = rep(19,5), xlab = "scaled metric", xlim = c(0,1))
dev.off()

pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_8d.pdf", height = 11, width = 8.5)
fancy.plot(raw_results_8d, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = rep(19,5), xlab = "scaled metric", xlim = c(0,1))
dev.off()

pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_emp.pdf", height = 11, width = 5.5)
fancy.plot(raw_results_emp, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = c(19,15,17), xlab = "scaled metric", xlim = c(0,1))
dev.off()
```

>>>>

```{r, echo = FALSE}
## Extracting all the scaled results
scaled_cent_results_2d <- extract.table(all_results_2d, scale.method = "between")
scaled_cent_results_3d <- extract.table(all_results_3d, scale.method = "between")
scaled_cent_results_4d <- extract.table(all_results_4d, scale.method = "between")
scaled_cent_results_5d <- extract.table(all_results_5d, scale.method = "between")
scaled_cent_results_8d <- extract.table(all_results_8d, scale.method = "between")
scaled_cent_results_emp<- extract.table(empirical_results, scale.method = "between")

scaled_cent_results_2d500 <- extract.table(all_results_2d500, scale.method = "between")
scaled_cent_results_4d500 <- extract.table(all_results_4d500, scale.method = "between")
scaled_cent_results_2d1000 <- extract.table(all_results_2d1000, scale.method = "between")
scaled_cent_results_4d1000 <- extract.table(all_results_4d1000, scale.method = "between")

## Extracting all the results but not centred (still scaled)
scaled_results_2d <- extract.table(all_results_2d, scale.method = "between", centre = FALSE)
scaled_results_3d <- extract.table(all_results_3d, scale.method = "between", centre = FALSE)
scaled_results_4d <- extract.table(all_results_4d, scale.method = "between", centre = FALSE)
scaled_results_5d <- extract.table(all_results_5d, scale.method = "between", centre = FALSE)
scaled_results_8d <- extract.table(all_results_8d, scale.method = "between", centre = FALSE)
scaled_results_emp<- extract.table(empirical_results, scale.method = "between", centre = FALSE)

scaled_results_2d500 <- extract.table(all_results_2d500, scale.method = "between", centre = FALSE)
scaled_results_4d500 <- extract.table(all_results_4d500, scale.method = "between", centre = FALSE)
scaled_results_2d1000 <- extract.table(all_results_2d1000, scale.method = "between", centre = FALSE)
scaled_results_4d1000 <- extract.table(all_results_4d1000, scale.method = "between", centre = FALSE)

## Extracting all the results not scaled
raw_results_2d <- extract.table(all_results_2d, scale = FALSE, centre = FALSE)
raw_results_3d <- extract.table(all_results_3d, scale = FALSE, centre = FALSE)
raw_results_4d <- extract.table(all_results_4d, scale = FALSE, centre = FALSE)
raw_results_5d <- extract.table(all_results_5d, scale = FALSE, centre = FALSE)
raw_results_8d <- extract.table(all_results_8d, scale = FALSE, centre = FALSE)
raw_results_emp<- extract.table(empirical_results, scale = FALSE, centre = FALSE)

raw_results_2d500 <- extract.table(all_results_2d500,scale = FALSE, centre = FALSE)
raw_results_4d500 <- extract.table(all_results_4d500, scale = FALSE, centre = FALSE)
raw_results_2d1000 <- extract.table(all_results_2d1000, scale = FALSE, centre = FALSE)
raw_results_4d1000 <- extract.table(all_results_4d1000, scale = FALSE, centre = FALSE)

@@

```{r, echo = FALSE}
## Slope and R2 for each model
model_fits_2d  <- lapply(scaled_cent_results_2d, fit.model.rm)
model_fits_3d  <- lapply(scaled_cent_results_3d, fit.model.rm)
model_fits_4d  <- lapply(scaled_cent_results_4d, fit.model.rm)
model_fits_5d  <- lapply(scaled_cent_results_5d, fit.model.rm)
model_fits_8d  <- lapply(scaled_cent_results_8d, fit.model.rm)
model_fits_emp <- lapply(scaled_cent_results_emp, fit.model.rm)

@@

## Making the fancy tables for the models
model_table_2d  <- fancy.table(model_fits_2d, columns = list(c(3,4), 5))
model_table_3d  <- fancy.table(model_fits_3d, columns = list(c(3,4), 5))
model_table_4d  <- fancy.table(model_fits_4d, columns = list(c(3,4), 5))
model_table_5d  <- fancy.table(model_fits_5d, columns = list(c(3,4), 5))
model_table_8d  <- fancy.table(model_fits_8d, columns = list(c(3,4), 5))
model_table_emp <- fancy.table(model_fits_emp, columns = list(c(3,4), 5))
## For the differences
columns_diff_ses <- list(c(1,3), 4)
columns_diff_ses <- c(columns_diff_ses,
                      lapply(columns_diff_ses, `+`, 4),
                      lapply(columns_diff_ses, `+`, 8),
                      lapply(columns_diff_ses, `+`, 12))
null_table_2d   <- fancy.table(null_differences_2d, columns = columns_diff_ses, digits = 2)
null_table_3d   <- fancy.table(null_differences_3d, columns = columns_diff_ses, digits = 2)
null_table_4d   <- fancy.table(null_differences_4d, columns = columns_diff_ses, digits = 2)
null_table_5d   <- fancy.table(null_differences_5d, columns = columns_diff_ses, digits = 2)
null_table_8d   <- fancy.table(null_differences_8d, columns = columns_diff_ses, digits = 2)
null_table_emp  <- fancy.table(null_differences_emp, columns = list(c(1,3), 4, c(1,3)+4, 4+4), digits = 2)

model_fits_2d500  <- lapply(scaled_cent_results_2d500, fit.model.rm)
null_differences_2d500  <- lapply(all_results_2d500, paired.tests)
model_table_2d500  <- fancy.table(model_fits_2d500, columns = list(c(3,4), 5))
null_table_2d500   <- fancy.table(null_differences_2d500, columns = columns_diff_ses, digits = 2)
model_fits_4d500  <- lapply(scaled_cent_results_4d500, fit.model.rm)
null_differences_4d500  <- lapply(all_results_4d500, paired.tests)
model_table_4d500  <- fancy.table(model_fits_4d500, columns = list(c(3,4), 5))
null_table_4d500   <- fancy.table(null_differences_4d500, columns = columns_diff_ses, digits = 2)

model_fits_2d1000  <- lapply(scaled_cent_results_2d1000, fit.model.rm)
null_differences_2d1000  <- lapply(all_results_2d1000, paired.tests)
model_table_2d1000  <- fancy.table(model_fits_2d1000, columns = list(c(3,4), 5))
null_table_2d1000   <- fancy.table(null_differences_2d1000, columns = columns_diff_ses, digits = 2)
model_fits_4d1000  <- lapply(scaled_cent_results_4d1000, fit.model.rm)
null_differences_4d1000  <- lapply(all_results_4d1000, paired.tests)
model_table_4d1000  <- fancy.table(model_fits_4d1000, columns = list(c(3,4), 5))
null_table_4d1000   <- fancy.table(null_differences_4d1000, columns = columns_diff_ses, digits = 2)

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
col_vector <- c(rep("darkgreen", 4), # The regularity ones
                rep("orange", 4), # The divergence ones
                rep("blue", 4)) # The richness ones
## The plot
fancy.plot(scaled_cent_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names, pch = rep(19,4), xlab = "scaled metric change", xlim = c(-1, 1))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_2d.pdf", height = 9, width = 9)
fancy.plot(scaled_cent_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names, pch = rep(19,4), xlim = c(-1, 1))
dev.off()
```

@@

```{r}
## The plot
fancy.plot(scaled_cent_results_3d, col = col_vector, lm = model_fits_3d, null = null_differences_3d, metric.names = fancy_names, pch = rep(19,4), xlim = c(-1, 1))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_3d.pdf", height = 9, width = 9)
fancy.plot(scaled_cent_results_3d, col = col_vector, lm = model_fits_3d, null = null_differences_3d, metric.names = fancy_names, pch = rep(19,4), xlim = c(-1, 1))
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_cent_results_4d, col = col_vector, lm = model_fits_4d, null = null_differences_4d, metric.names = fancy_names, pch = rep(19,4), xlim = c(-1, 1))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_4d.pdf", height = 9, width = 9)
fancy.plot(scaled_cent_results_4d, col = col_vector, lm = model_fits_4d, null = null_differences_4d, metric.names = fancy_names, pch = rep(19,4), xlim = c(-1, 1))
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_cent_results_5d, col = col_vector, lm = model_fits_5d, null = null_differences_5d, metric.names = fancy_names, pch = rep(19,4), xlim = c(-1, 1))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_5d.pdf", height = 9, width = 9)
fancy.plot(scaled_cent_results_5d, col = col_vector, lm = model_fits_5d, null = null_differences_5d, metric.names = fancy_names, pch = rep(19,4), xlim = c(-1, 1))
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_cent_results_8d, col = col_vector, lm = model_fits_8d, null = null_differences_8d, metric.names = fancy_names, pch = rep(19,4), xlim = c(-1, 1))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_8d.pdf", height = 9, width = 9)
fancy.plot(scaled_cent_results_8d, col = col_vector, lm = model_fits_8d, null = null_differences_8d, metric.names = fancy_names, pch = rep(19,4), xlim = c(-1, 1))
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_cent_results_emp, col = col_vector, lm = NULL, null = null_differences_emp, metric.names = fancy_names, pch = c(19,15,17), xlim = c(-1, 1))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_emp.pdf", height = 11, width = 3.5)
fancy.plot(scaled_cent_results_emp, col = col_vector, lm = NULL, null = null_differences_emp, metric.names = fancy_names, pch = c(19,15,17), xlim = c(-1, 1))
dev.off()
```

@@

```{r}
## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_2d500.pdf", height = 9, width = 9)
fancy.plot(scaled_cent_results_2d500, col = col_vector, lm = model_fits_2d500, null = null_differences_2d500, metric.names = fancy_names, pch = rep(19,4), xlim = c(-1, 1))
dev.off()

pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_4d500.pdf", height = 9, width = 9)
fancy.plot(scaled_cent_results_4d500, col = col_vector, lm = model_fits_4d500, null = null_differences_4d500, metric.names = fancy_names, pch = rep(19,4), xlim = c(-1, 1))
dev.off()

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_2d1000.pdf", height = 9, width = 9)
fancy.plot(scaled_cent_results_2d1000, col = col_vector, lm = model_fits_2d1000, null = null_differences_2d1000, metric.names = fancy_names, pch = rep(19,4), xlim = c(-1, 1))
dev.off()

pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_4d1000.pdf", height = 9, width = 9)
fancy.plot(scaled_cent_results_4d1000, col = col_vector, lm = model_fits_4d1000, null = null_differences_4d1000, metric.names = fancy_names, pch = rep(19,4), xlim = c(-1, 1))
dev.off()
```

@@

pdf(file = "../Manuscript/Figures/scaled_results_per_metric_per_stressor_2d.pdf", height = 11, width = 8.5)
fancy.plot(scaled_results_2d, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = rep(19,5), xlab = "scaled metric", xlim = c(0,1))
dev.off()

pdf(file = "../Manuscript/Figures/scaled_results_per_metric_per_stressor_4d.pdf", height = 11, width = 8.5)
fancy.plot(scaled_results_4d, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = rep(19,5), xlab = "scaled metric", xlim = c(0,1))
dev.off()

pdf(file = "../Manuscript/Figures/scaled_results_per_metric_per_stressor_8d.pdf", height = 11, width = 8.5)
fancy.plot(scaled_results_8d, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = rep(19,5), xlab = "scaled metric", xlim = c(0,1))
dev.off()

pdf(file = "../Manuscript/Figures/scaled_results_per_metric_per_stressor_emp.pdf", height = 11, width = 5.5)
fancy.plot(scaled_results_emp, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = c(19,15,17), xlab = "scaled metric", xlim = c(0,1))
dev.off()
```

```{r}
# pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_2d.pdf", height = 11, width = 8.5)

# layout(matrix(1:(12*5), 12, 5))
# for(stressor in 1:5) {
#     ## For each stressor
#     plotting_data <- raw_results_2d[[stressor]]
#     ## Plot the metric
#     for(one_metric in 1:(ncol(plotting_data)/4)) {
#         ## Get the metric name
#         metric_name <- strsplit(colnames(selected_data), split = "_rm")[[1]][1]
#         ## Get the data
#         selected_data <- plotting_data[, 1:4]

#         ## Get the color TODO + add transparent
#         col <- rep("orange", 4)

#         ## Empty plot
#         plot(NULL, ylim = c(0, 5), xlim = quantile(c(selected_data), prob =  c(0.025, 0.975)), yaxt = "n", ylab = "", xlab = metric_name)

#         ## Add the lines
#         for(one_line in 1:4) {
#             ## Get the CIs and median
#             CIs <- quantile(selected_data[, one_line], prob = c(0.025, 0.25, 0.75, 0.975))
#             med <- median(selected_data[, one_line])
#             ## Plot the CIs
#             lines(y = rep(5-one_line, 2), x = CIs[c(1, 4)], lty = 3, col = col)
#             lines(y = rep(5-one_line, 2), x = CIs[c(2, 3)], lty = 1, col = col)
#             ## Plot the median
#             points(y =5-one_line, x = med, pch = 19, col = col)
#         }
#     }
# }

# fancy.plot(raw_results_2d, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = rep(19,5), xlab = "raw metric")
# dev.off()

# pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_4d.pdf", height = 11, width = 8.5)
# fancy.plot(raw_results_4d, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = rep(19,5), xlab = "raw metric")
# dev.off()

# pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_8d.pdf", height = 11, width = 8.5)
# fancy.plot(raw_results_8d, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = rep(19,5), xlab = "raw metric")
# dev.off()

# pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_emp.pdf", height = 11, width = 5.5)
# fancy.plot(raw_results_emp, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = c(19,15,17), xlab = "raw metric")
# dev.off()
```
